Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-08-17 vesicle_code/docs/permeableVes/main.tex
adding new figure to pnas paper

>>>>

\begin{figure}[htp]
  \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
  \caption{\label{fig:parabolicOffCenterPhaseDiagram} Phase diagram of
  an impermeable vesicle with several different flow rates $U$ and
  reduced areas $\nu$. As shown by Kaoui et al.~\cite{kao-bir-mis2009},
  the final vesicle shape is either an asymmetric parachute or bullet
  (pink region) or a axisymmetric slipper (yellow region).}
\end{figure}
